Ethnicity sensitive author disambiguation using semi-supervised learning

### 2016-01-12 paper/author_disambiguation.tex
Revert eg change
Signed-off-by: Mateusz Susik <mateuszsusik@gmail.com>

To account for these issues we propose instead to block signatures based on the
phonetic representation of the normalized surname.
Normalization involves stripping accents (e.g., "Jab\l{}o\'nski, \L{}" $\rightarrow$ "Jablonski, L") and name
affixes that inconsistently appear in signatures (e.g., "van der Waals, J. D."
$\rightarrow$ "Waals, J. D."), while phonetization is based either on the
Double Metaphone \cite{doublemetaphone}, the NYSIIS \cite{nysiis} or the
Soundex \cite{Soundex} phonetic algorithms for mapping author names to their pronunciations.
Together, these processing steps allow for grouping of most name variants of the same
person in the same block with a small increase in the overall computational complexity, thereby solving case 1.

>>>>

To account for these issues we propose instead to block signatures based on the
phonetic representation of the normalized surname.
Normalization involves stripping accents (\eg, "Jab\l{}o\'nski, \L{}" $\rightarrow$ "Jablonski, L") and name
affixes that inconsistently appear in signatures (\eg, "van der Waals, J. D."
$\rightarrow$ "Waals, J. D."), while phonetization is based either on the
Double Metaphone \cite{doublemetaphone}, the NYSIIS \cite{nysiis} or the
Soundex \cite{Soundex} phonetic algorithms for mapping author names to their pronunciations.
Together, these processing steps allow for grouping of most name variants of the same
person in the same block with a small increase in the overall computational complexity, thereby solving case 1.
